Atlantis to SS for California Current sardines and hake: full fishing and climate scenario

### 2019-10-01 SardinesHakeatlantisom2SStest.Rmd
clarify what works and doesnt
working ss run

Below we get the weight-length relationship parameters from atlantis, calculate h and R0 from Atlantis $\alpha$ and $\beta$ parameters, use the \code{calc_Z} function to back out natural mortality (M) from Atlantis, and use the survey length-at-age from Atlantis to estimate a growth curve.
```{r, eval=FALSE}
#Get biological parameters

@@

```{r runSS, eval=FALSE}
#Run stock synthesis model 
run_stocksynthesis(species = species, model_dir = model_dir, show_output = TRUE)

>>>>

Below we get the weight-length relationship parameters from atlantis, calculate h and R0 from Atlantis $\alpha$ and $\beta$ parameters, use the \code{calc_Z} function to back out natural mortality (M) from Atlantis, and use the survey length-at-age from Atlantis to estimate a growth curve.

The following is under construction from CreateStockSynthesis.Rmd and not evaluated. Existing control file was modified by hand to make the number of recruitment settlement assignments 1 instead of two, with GPattern month area age vector 1 1 1 1.

```{r, eval=FALSE}
#Get biological parameters

@@

```{r runSS, eval=FALSE}
#Run stock synthesis model 
# default runs with admb_options = "-noest"
#run_stocksynthesis(species = species, model_dir = model_dir, show_output = TRUE)

# for estimation
run_stocksynthesis(species = species, model_dir = model_dir, admb_options = "", show_output = TRUE)
